---
title: "QUK2 SH WJ Leak Test Data Exploratory Analysis"
author: "Jim Yan"
date: "30 March 2018"
output:
  html_document:
    df_print: paged
---

```{r setup, include=FALSE}
# turn on cache
knitr::opts_chunk$set(cache=TRUE)
```

```{r Preparation,  message=FALSE, warning=FALSE,echo=FALSE}
# Install & load required packages
source("ExploratoryAnalysisMoudle.R")

Required_Packages=c("openxlsx", "data.table", "splitstackshape", "dplyr","tidyr", "lubridate","ggplot2", "scales", "plotly", "mlr")
Install_And_Load(Required_Packages)
```

## QUK2 SH WJ Air Decay Leak Test - Water Passsage Section

### Dataset at glance

Data was extrated from raw data by running script "0-ExtractCleanData-LeakTestStation.R".

Remarks of the extraction process:

* Duplicates was not removed.
* All processed data include duplicates and was sorted in order of time/part_id. 
* Data from the same file will be subset into 3 different data set with similar structure.
* Within the same table, the Rows contained NA was removed.

Datasets were saved into below files:

* DataOutput/dt.AirDecay.WP.Full.RDS
* DataOutput/dt.AirDecay.MC.Full.RDS
* DataOutput/dt.AirDecay.He.Full.RDS

```{r, message=FALSE, warning=FALSE}
      dt.AirDecay.WP.NoMaster <- readRDS("DataOutput/dt.AirDecay.WP.NoMaster.RDS")
      ## Check data summary
      summarizeColumns(dt.AirDecay.WP.NoMaster)
```

Found that there were missing values on casting date due to wrong barcode format. We need to remove those part with incorrect ID.

```{r, message=FALSE, warning=FALSE}
      dt.AirDecay.WP.NoMaster <- dt.AirDecay.WP.NoMaster[complete.cases(dt.AirDecay.WP.NoMaster),]
      ## Check data summary
      summarizeColumns(dt.AirDecay.WP.NoMaster)
```

Now summarizing the daily statics of the leak rate.

```{r AllDailyChart 2017-2018,  fig.width=10, fig.height=8, echo=FALSE}
      
```

***

```{r}

```

