---
title: "QUK2 SH WJ Leak Test Data Exploratory Analysis"
author: "Jim Yan"
date: "30 March 2018"
output:
  html_document:
    df_print: paged
---

```{r setup, include=FALSE}
# turn on cache
knitr::opts_chunk$set(cache=TRUE)
```

```{r Preparation,  message=FALSE, warning=FALSE,echo=FALSE}
# Install & load required packages
source("ExploratoryAnalysisMoudle.R")

Required_Packages=c("openxlsx", "data.table", "splitstackshape", "dplyr","tidyr", "lubridate","ggplot2", "scales", "plotly", "mlr", "psych")
Install_And_Load(Required_Packages)
```

## QUK2 SH WJ Air Decay Leak Test - Water Passsage Section

### Dataset at glance

Data was extrated from raw data by running script "0-ExtractCleanData-LeakTestStation.R".

Remarks of the extraction process:

* Duplicates was not removed.
* All processed data include duplicates and was sorted in order of time/part_id. 
* Data from the same file will be subset into 3 different data set with similar structure.
* Within the same table, the Rows contained NA was removed.

Datasets were saved into below files:

* DataOutput/dt.AirDecay.WP.Full.RDS
* DataOutput/dt.AirDecay.MC.Full.RDS
* DataOutput/dt.AirDecay.He.Full.RDS

```{r, message=FALSE, warning=FALSE, echo=FALSE}
      dt.AirDecay.WP.NoMaster <- readRDS("DataOutput/dt.AirDecay.WP.NoMaster.RDS")
      ## Check data summary
      # summarizeColumns(dt.AirDecay.WP.NoMaster)

      ## Found that there were missing values on casting date due to wrong barcode format. We need to remove those part with incorrect ID.
      dt.AirDecay.WP.NoMaster <- dt.AirDecay.WP.NoMaster[complete.cases(dt.AirDecay.WP.NoMaster),]
      ## Check data summary
      # summarizeColumns(dt.AirDecay.WP.NoMaster)
```

***

### Observation Leak Rate from Jan2018 to Mar2018

Now summarizing the daily statics of the leak rate from JAN/2018 to Mar/2018.

```{r AllDailyChart 2018,  fig.width=10, fig.height=8, echo=FALSE}
      ## Remove duplicates, calculate leak test result based on supplied spec.
      ## Run statics on data on daily basis.
      dt.Daily.Statics.AirDecay.WP.NoMaster <- Daily.Statics.AirDecay.WP(dt.AirDecay.WP.NoMaster, -3, 2.1 )

      dt.Daily.Statics.AirDecay.WP.NoMaster.2018 <- dt.Daily.Statics.AirDecay.WP.NoMaster[dt.Daily.Statics.AirDecay.WP.NoMaster$Date >= as.Date("2018-01-01"),]

      g.Mean.2018 <- Plot.LineChart.Year(dt.Daily.Statics.AirDecay.WP.NoMaster.2018, "Date", "Avg.LeakRate", 0, -3, 2.1,
                                      mean(dt.Daily.Statics.AirDecay.WP.NoMaster.2018$Avg.LeakRate),
                                      sd(dt.Daily.Statics.AirDecay.WP.NoMaster.2018$Avg.LeakRate),
                                      "WP Leak Rate Statics - Daily Mean Chart")
      
      g.SD.2018 <- Plot.LineChart.Year(dt.Daily.Statics.AirDecay.WP.NoMaster.2018, "Date", "Stdev.LeakRate", 0, 0, 0,
                                      mean(dt.Daily.Statics.AirDecay.WP.NoMaster.2018$Stdev.LeakRate),
                                      sd(dt.Daily.Statics.AirDecay.WP.NoMaster.2018$Stdev.LeakRate),
                                      "WP Leak Rate Statics - Daily Sigma Chart")
      
      g.NGRate.2018 <- Plot.LineChart.Year(dt.Daily.Statics.AirDecay.WP.NoMaster.2018, "Date", "RejectPrecent", 0, 0, 0,
                                    mean(dt.Daily.Statics.AirDecay.WP.NoMaster.2018$RejectPrecent),
                                    sd(dt.Daily.Statics.AirDecay.WP.NoMaster.2018$RejectPrecent),
                                    "WP Leak Rate Statics - Daily Reject Precentage Chart")
      
      g.qty.2018 <- Plot.LineChart.Year(dt.Daily.Statics.AirDecay.WP.NoMaster.2018, "Date", "Qty", 0, 0, 0,
                                 mean(dt.Daily.Statics.AirDecay.WP.NoMaster.2018$Qty),
                                 sd(dt.Daily.Statics.AirDecay.WP.NoMaster.2018$Qty),
                                 "WP Leak Rate Statics - Daily Reject Qty. Chart")
      
      multiplot(g.Mean.2018, g.SD.2018, g.NGRate.2018, g.qty.2018, cols=1)
```

***

### Establish Contorl Limit of Leak Rate

Establishing contorl limits from goods dates in 2018: 10/JAN/2018 to 16/JAN/2018, 1~4/FEB, 20/FEB, 22/FEB. 
```{r ControlLimit,   warning=FALSE, echo=FALSE}
date.good <- data.frame(Date = c(as.Date("2018-01-10"), as.Date("2018-01-11"), as.Date("2018-01-12"), as.Date("2018-01-13"),
                                 as.Date("2018-01-14"), as.Date("2018-01-15"), as.Date("2018-01-16"), as.Date("2018-02-01"),
                                 as.Date("2018-02-02"), as.Date("2018-02-03"), as.Date("2018-02-04"), as.Date("2018-02-20"),
                                 as.Date("2018-02-22")))

dt.good <- dt.AirDecay.WP.NoMaster[date(dt.AirDecay.WP.NoMaster$LeakTestDateTime) %in% date.good[,1], ]
dt.good <- dt.good[order(dt.good$LeakTestDateTime, decreasing = FALSE),]

#Remove duplicates
dt.good <- dt.good[ , .SD[.N] ,  by = c("part_id") ]
# describe(dt.good)

# Setup control mean and sigma
Mean.Control.WP <- mean(dt.good$air_decay_wp)
Sigma.Control.WP <- sd(dt.good$air_decay_wp)

```

Contorl Limits of leak rate was set as below:

* Mean Contorl Limit = `r Mean.Control.WP`
* Sigma Contorl Limit = `r Sigma.Control.WP`

***

### Observation Leak Rate from Jan2017 to Mar2018

Now summarizing the daily statics of the leak rate from JAN/2017 to Mar/2018.
```{r AllDailyChart 2017-2018,  fig.width=10, fig.height=12, echo=FALSE}
      ## Remove duplicates, calculate leak test result based on supplied spec.
      ## Run statics on data on daily basis.
      # dt.Daily.Statics.AirDecay.WP.NoMaster <- Daily.Statics.AirDecay.WP(dt.AirDecay.WP.NoMaster, -3, 2.1 )

      g.Mean <- Plot.LineChart.Year(dt.Daily.Statics.AirDecay.WP.NoMaster, "Date", "Avg.LeakRate", 0, -3, 2.1,
                                      Mean.Control.WP,
                                      Sigma.Control.WP,
                                      "WP Leak Rate Statics - Daily Mean Chart")
      
      g.SD <- Plot.LineChart.Year(dt.Daily.Statics.AirDecay.WP.NoMaster, "Date", "Stdev.LeakRate", 0, 0, 0,
                                      mean(dt.Daily.Statics.AirDecay.WP.NoMaster$Stdev.LeakRate),
                                      sd(dt.Daily.Statics.AirDecay.WP.NoMaster$Stdev.LeakRate),
                                      "WP Leak Rate Statics - Daily Sigma Chart")
      
      g.NGRate <- Plot.LineChart.Year(dt.Daily.Statics.AirDecay.WP.NoMaster, "Date", "RejectPrecent", 0, 0, 0,
                                    mean(dt.Daily.Statics.AirDecay.WP.NoMaster$RejectPrecent),
                                    sd(dt.Daily.Statics.AirDecay.WP.NoMaster$RejectPrecent),
                                    "WP Leak Rate Statics - Daily Reject Precentage Chart")
      
      g.qty <- Plot.LineChart.Year(dt.Daily.Statics.AirDecay.WP.NoMaster, "Date", "Qty", 0, 0, 0,
                                 mean(dt.Daily.Statics.AirDecay.WP.NoMaster$Qty),
                                 sd(dt.Daily.Statics.AirDecay.WP.NoMaster$Qty),
                                 "WP Leak Rate Statics - Daily Reject Qty. Chart")
      
      multiplot(g.Mean, g.SD, g.NGRate, g.qty, cols=1)
```

***

### Observation - leak rate in Jan-17

Subset data from "2017-01-11" to "2017-01-29" for observation. Ploted the hourly statics. Observed 2 period of time with high variation on leak rate and reject rate:

* 03~06 JAN 2017;
* 11~13 JAN 2017;

The basics statics of this dataset is present as below:
```{r, echo=FALSE}
        dt.P1 <- dt.AirDecay.WP.NoMaster[date(dt.AirDecay.WP.NoMaster$LeakTestDateTime) >= as.Date("2017-01-01") 
                                      & date(dt.AirDecay.WP.NoMaster$LeakTestDateTime) <= as.Date("2017-01-29") ,]

        Sum.Stat.AirDecay.WP(dt.P1)
        
```


```{r,  fig.width=10, fig.height=12, echo=FALSE}
        dt.Hourly.Statics.P1 <- Hourly.Statics.AirDecay.WP(dt.P1, -3, 2.1 )
        
        g.Mean.P1 <- Plot.LineChart.Hour(dt.Hourly.Statics.P1, "HourDate", "Avg.LeakRate", 0, -3, 2.1,
                                 mean(dt.Hourly.Statics.P1$Avg.LeakRate),
                                 sd(dt.Hourly.Statics.P1$Avg.LeakRate),
                                 "WP Leak Rate Statics - Hourly Sigma Chart")
        
        g.Mean.P1 <- g.Mean.P1 + 
                      annotate("rect", xmin=as.POSIXct(as.Date("2017-01-03")), xmax=as.POSIXct(as.Date("2017-01-07")), 
                                ymin=-1, ymax=5, alpha=.1,fill="blue") + 
                      annotate("text", label="3~6/JAN 2017: \nHigh Leak Rate\n Variation & \nReject Rate", x=as.POSIXct(as.Date("2017-01-05")), y=4 ) +
                      annotate("rect", xmin=as.POSIXct(as.Date("2017-01-11")), xmax=as.POSIXct(as.Date("2017-01-14")), 
                               ymin=-1, ymax=5, alpha=.1,fill="blue") +
                      annotate("text", label="11~13/JAN 2017: \nHigh Leak Rate\n Variation & \nReject Rate", x=as.POSIXct(as.Date("2017-01-12")), y=4 )
          
        g.SD.P1 <- Plot.LineChart.Hour(dt.Hourly.Statics.P1, "HourDate", "Stdev.LeakRate", 0, 0, 0,
                                             mean(dt.Hourly.Statics.P1$Stdev.LeakRate),
                                             sd(dt.Hourly.Statics.P1$Stdev.LeakRate),
                                             "WP Leak Rate Statics - Hourly Mean Chart")

        g.SD.P1 <- g.SD.P1 + 
                      annotate("rect", xmin=as.POSIXct(as.Date("2017-01-03")), xmax=as.POSIXct(as.Date("2017-01-07")), 
                               ymin=-1, ymax=10, alpha=.1,fill="blue") + 
                      annotate("rect", xmin=as.POSIXct(as.Date("2017-01-11")), xmax=as.POSIXct(as.Date("2017-01-14")), 
                               ymin=-1, ymax=10, alpha=.1,fill="blue") 

        g.NGRate.P1 <- Plot.LineChart.Hour(dt.Hourly.Statics.P1, "HourDate", "RejectPrecent", 0, 0, 0,
                                             mean(dt.Hourly.Statics.P1$RejectPrecent),
                                             sd(dt.Hourly.Statics.P1$RejectPrecent),
                                             "WP Leak Rate Statics - Hourly Reject Precentage Chart")

        g.NGRate.P1 <- g.NGRate.P1 + 
                          annotate("rect", xmin=as.POSIXct(as.Date("2017-01-03")), xmax=as.POSIXct(as.Date("2017-01-07")), 
                                   ymin=-1, ymax=50, alpha=.1,fill="blue") + 
                          annotate("rect", xmin=as.POSIXct(as.Date("2017-01-11")), xmax=as.POSIXct(as.Date("2017-01-14")), 
                                   ymin=-1, ymax=50, alpha=.1,fill="blue") 
                
        g.qty.P1 <- Plot.LineChart.Hour(dt.Hourly.Statics.P1, "HourDate", "Qty", 0, 0, 0,
                                             mean(dt.Hourly.Statics.P1$Qty),
                                             sd(dt.Hourly.Statics.P1$Qty),
                                             "WP Leak Rate Statics - Hourly Reject Qty. Chart")

        g.qty.P1 <- g.qty.P1 + 
                        annotate("rect", xmin=as.POSIXct(as.Date("2017-01-03")), xmax=as.POSIXct(as.Date("2017-01-07")), 
                                 ymin=-1, ymax=30, alpha=.1,fill="blue") + 
                        annotate("rect", xmin=as.POSIXct(as.Date("2017-01-11")), xmax=as.POSIXct(as.Date("2017-01-14")), 
                                 ymin=-1, ymax=30, alpha=.1,fill="blue") 
        
        multiplot(g.Mean.P1, g.SD.P1, g.NGRate.P1, g.qty.P1, cols=1)
```

***

### Observation - leak rate in 03~06/Jan/17

```{r,  fig.width=10, fig.height=12, echo=FALSE}

```
